Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
move Hspec explanation to footnote.

If we have evidence that does not fit into the user documentation, but
would rather be part of a design document, we use Hspec.

\begin{quote}
    Hspec was originally implemented by Trystan Spangler, and is now
    maintained and actively/further developed by one of the authors.

    \emph{sol: Do you think we should include this here? Is it
    relevant? If it is relevant, it would probably better fit in to
    the ``Introduction'', right?}
\end{quote}

>>>>

If we have evidence that does not fit into the user documentation, but
would rather be part of a design document, we use Hspec\footnote{%
Hspec was originally implemented by Trystan Spangler, and is now
maintained and actively/further developed by one of the authors.}.
